Effects of sexual selection on non-sexual fitness components: a meta-analysis

### 2018-04-12 meta_analysis_sexual_selection_pop_fitness.Rmd
12/4/18 update

```{r warning=FALSE, message=FALSE, results='hide'}
library(knitr)
library(pander)
library(compute.es)
library(metafor)
library(dplyr)
library(lme4)
library(forestplot)
library(ggplot2)
library(kableExtra)
library(ggrepel)
library(reshape2)
library(RColorBrewer)
source("Vdodge_function.R") # nice function for ggplot
```

@@

@@

ggsave(plot = generations.plot, filename = "figures/generations_plot.eps", height = 7.5, width = 10)
generations.plot
```
<br></br>
**Figure S10:** The number of generations an experimental evolution procedure is run for does not appear to affect the magnitude or direction of the effect size from the fitness related outcome measured at that point.

>>>>

```{r, warning=FALSE, message=FALSE, results='hide'}
library(pander)
library(compute.es)
library(metafor)
library(dplyr)
library(lme4)
library(forestplot)
library(ggplot2)
library(kableExtra)
library(ggrepel)
library(reshape2)
library(RColorBrewer)
source("Vdodge_function.R") # nice function for ggplot
```

@@

```{r}
head(outcome.descriptions)
```

@@

ggsave(plot = generations.plot, filename = "figures/generations_plot.eps", height = 7.5, width = 10)
generations.plot
```
<br></br>
**Figure S10:** The number of generations an experimental evolution procedure is run for does not appear to affect the magnitude or direction of the effect size from the fitness related outcome measured at that point. 
<br></br>

Kawecki et al.(2012) reviewed the field of experimental evolution and noted that changes to variation may need longer generations to become apparent. The following graph looks at the relationship between number of generations and lnCVr

```{r, fig.height= 7.5, fig.width=10, warning=FALSE}
generations.plot.var <- prelim.data2 %>% ggplot(aes(x=Generations, y=lnCVr))+
  geom_point(shape=21, color = "grey20", size=2, aes(fill=Taxon))+
  ylim(-3.5,3.5)+
  geom_hline(yintercept=0, linetype="dashed") + 
  scale_fill_brewer(palette = "Set3")+
  geom_smooth(method = 'lm', color='black')+
  labs(y='Effect size (lnCVR)', x= 'Generations', size= 'Weight (%)')

# ggsave(plot = generations.plot, filename = "figures/generations_plot.eps", height = 7.5, width = 10)
generations.plot.var
```

**Figure S11:** WRITE HERE
